\bf\mftitle

### 2011-03-02 doc/jInfer/projecttype/projecttype.tex
last minute corrections + PDF almost done

\begin{document}
\maketitle
\noindent Target audience: developers willing to extend jInfer, specifically extend jInfer project structure.

@@

\begin{figure}
	\subfigure[Legend: Rectangle is folder, Rounded rectangle is file.] {
		\centering\includegraphics[scale=\myscale]{project_dir_structure}
	}
	\caption{Project directory structure.} \label{dir-structure}
\end{figure}

For each jInfer project a specific directory structure in the filesystem describing this project is created. This structure is described in figure \ref{dir-structure}. A folder in the filesystem is considered to be jInfer project folder if it contains a \emph{jinferproject} subfolder. This folder contains two files: \emph{project.properties}, where all properties set for that particular project are stored. The second file is \emph{input.files} which is an XML file filled with paths to files selected as particular project input (structure of this file is described in section \ref{input.files}). \emph{output} subfolder contains schema files which were generated by jInfer inference runs.

@@

\code{InputFiles} is a utility class that stores/loads input file paths into/from the \emph{input.files} XML file. For this purpose, \code{InputFiles} uses \emph{JAXB} \cite{JAXB} framework to unmarshall/marshall XML file into/from Java content objects. XML structure of \emph{input.files} is very simple, \emph{jinferinput} is the root element under which are \emph{documents}, \emph{schemas} and \emph{queries} elements. Each of this elements may have none or more \emph{file} elements with string attribute \emph{loc} that contains the absolute path to the input file.\\

@@

Each jInfer project in NBP is open after its creation in the Projects view and has tree structure where each node is represented by a NBP \code{Node} class. This structure in jInfer project type is provided by the \code{JInferLogicalView} class implementing \code{LogicalViewProvider} interface from NBP and is available through the \code{JInferProject} lookup. This class has one important method: \code{createLogicalView()} returning an instance of \code{RootNode} class. Simple class structure is described in figure \ref{node-structure}.\\

>>>>

\begin{document}
\maketitle
\noindent Target audience: developers willing to extend jInfer, specifically to extend jInfer project structure.

@@

\begin{figure}
	\subfigure[Legend: Rectangle represents a folder and rounded rectangle a file.] {
		\centering\includegraphics[scale=\myscale]{project_dir_structure}
	}
	\caption{Project directory structure.} \label{dir-structure}
\end{figure}

For each jInfer project a specific directory structure in the filesystem describing this project is created. This structure is described in figure \ref{dir-structure}. A folder in the filesystem is considered to be jInfer project folder if it contains a \emph{jinferproject} subfolder. This folder contains two files: \emph{project.properties}, where all properties set for that particular project are stored. The second file is \emph{input.files} which is an XML file filled with paths to files selected as particular project input (structure of this file is described in section \ref{input.files}). \emph{Output} subfolder contains schema files which were generated by jInfer inference runs.

@@

\code{InputFiles} is a utility class that stores/loads input file paths into/from the \emph{input.files} XML file. For this purpose, \code{InputFiles} uses \emph{JAXB} \cite{JAXB} framework to marshall or unmarshall XML file to, and from, the Java content objects. XML structure of \emph{input.files} is very simple, \emph{jinferinput} is the root element under which are \emph{documents}, \emph{schemas} and \emph{queries} elements. Each of this elements may have none or more \emph{file} elements with string attribute \emph{loc} that contains the absolute path to the input file.\\

@@

Each jInfer project in NBP is open after its creation in the Projects view and has a tree structure where each node is represented by a NBP \code{Node} class. This structure in jInfer project type is provided by the \code{JInferLogicalView} class implementing \code{LogicalViewProvider} interface from NBP and is available through the \code{JInferProject} lookup. This class has one important method: \code{createLogicalView()} returning an instance of \code{RootNode} class. Simple class structure is described in figure \ref{node-structure}.\\
